Title Goes Here

### 2020-05-15 analysis/paper/paper.Rmd
working on background section

When focusing on the field of archaeology, we can see that gender imbalance still occurs in archaeology and that seems to impact the kind of publications that are done in the field [@bardolph2014critical]. In a previous study done on gender balance of the production of the Atapuerca Project, a project about human evolution in the field of archaeo-palaeontology, they have found that among all the authors, only 35.9% of them are women [@rodriguez2018gender]. In our study, we also continue the study of gender distribution of presenters at major archaeological conferences.

Another similar imbalance can be seen in terms of the authorship of articles or papers written. For example, for the authorship of the main authors from the Journal of Field Archaeology, 78% of them are men. [@heath2020guest]. This can also be seen in the study of the Atapuerca Project, in which only 34.8% of the papers are written by a female first/lead author [@rodriguez2018gender]. We have extended the study of ratios of authorships in the field of archaeology by specifically focusing on the gender imbalance that occurs in the topics that the authors present in major archaeological conferences.

When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership and the gender gap is almost gone. Although this similar trend is also present in the study by @vanderwarker2018ucsb in terms of more and more women pursuing a degree in archaeology than men, it is important to note that data collected from University of California, Santa Barbara Gender Equity Project shows that there are still imbalance as a result of different pay rates, professional ranking, and professional advancement [@gonzalez2018perceptions].

>>>>

When focusing on the field of archaeology, we can see that gender imbalance still occurs in archaeology and that seems to impact the kind of publications that are done in the field [@bardolph2014critical]. @rodriguez2018gender studied gender balance among 309 authors of 299 publications produced during 1978-2016 by the Atapuerca Project, a large archaeo-palaeontological project in Burgos, Spain. They 'manually defined' the gender of each author, and found 13 articles authored exclusively by women, 34.8% of papers have women as first-authors, and overall, 35.9% of all authors are women [@rodriguez2018gender]. Over time, they observed a trend of increasing numbers of papers that include women as authors, numbers of paper lead by women as the first author, and increases in the ratio of female to male authors in group-authored papers. They did not make any observations about relationships between gender and topics.

Another similar imbalance can be seen in terms of the authorship of articles or papers written. For example, for the authorship of the first authors of 1,104 articles published in the _Journal of Field Archaeology_ during 1974–2018, 72% of them are men [@heath2020guest].  We have extended the study of ratios of authorships in the field of archaeology by specifically focusing on the gender imbalance that occurs in the topics that the authors present in major archaeological conferences.

<!-- change over time -->
When looking at gender ratios among the membership in Society for California Archaeology from 1967 to 2016, @tushingham2017peer report a trend of women increasingly maintaining their society membership and the gender gap is almost gone. Although this similar trend is also present in the study by @vanderwarker2018ucsb in terms of more and more women pursuing a degree in archaeology than men, it is important to note that data collected from University of California, Santa Barbara Gender Equity Project shows that there are still imbalance as a result of different pay rates, professional ranking, and professional advancement [@gonzalez2018perceptions].

<!-- add one more -->
